Reducing retrieval error in MAIAC AOD with the `Earth_obs_cleaning` machine-learning workflow: Results from CONUS

### 2023-08-22 writing/CONUS_AOD.qmd
Changed the appearance of the agreement plot.

```{r agreement_plot, dev='png', dpi=300}
agreement.plot = \(vname.pred)
   {d = dt[, .(y.ground, y.pred = get(vname.pred))]
    i = d[, between(y.ground, 0, 1) & between(y.pred, 0, 1)]
    sample.obs = data.table(y.ground = seq(0, 1, len = 1000))
    ps = empirical.error.envelope(obs = d$y.ground, d$y.pred)$par
    sample.obs[, envelope.hi := y.ground + ps[1] + ps[2]*y.ground]
    sample.obs[, envelope.lo := y.ground - ps[1] - ps[2]*y.ground]
    ggplot() +
        geom_pointdensity(data = d, aes(y.ground, y.pred),
            alpha = 0.1, size = 0.6) +
        geom_abline(linetype = "dashed") +
        geom_line(data = sample.obs, aes(y.ground, envelope.hi)) +
        geom_line(data = sample.obs, aes(y.ground, envelope.lo)) +
        xlab("AERONET AOD 470nm") +
        ylab("MAIAC AOD 470nm") +
        guides(color = "none") +
        theme_bw() +
        coord_equal(xlim = c(0, 1), ylim = c(0, 1), expand = F) +
        labs(caption = paste0("Not shown: ", d[!i, .N], " AOD values outside [0, 1]"))}

agreement.plot("y.sat") + agreement.plot("y.ground.pred")
```

>>>>

```{r agreement_plot, dev='png', dpi=300}
(\()
   {d = melt(dt[, .(y.ground, y.ground.pred, y.sat)],
        id = "y.ground", variable.name = "comparison", value.name = "y.pred")
    d[, comparison := factor(comparison, levels = rev(levels(comparison)))]
    d[, in.region := between(y.ground, 0, 1) & between(y.pred, 0, 1)]
    sample.obs = `[`(
        CJ(
            comparison = unique(d$comparison),
            y.ground = seq(0, 1, len = 1000)),
        by = comparison,
        j =
           {ps = with(d[comparison == .BY$comparison],
                empirical.error.envelope(obs = y.ground, y.pred)$par)
            punl(
                y.ground,
                envelope.hi = y.ground + ps[1] + ps[2]*y.ground,
                envelope.lo = y.ground - ps[1] - ps[2]*y.ground)})
    ggplot() +
        geom_pointdensity(data = d[(in.region)], aes(y.ground, y.pred),
            size = 1/4, adjust = 1/2) +
        scale_color_gradient(low = "#dddddd", high = "black") +
        geom_abline(linetype = "dashed", color = "#6666aa") +
        geom_line(data = sample.obs, aes(y.ground, envelope.hi),
            color = "#6666aa") +
        geom_line(data = sample.obs, aes(y.ground, envelope.lo),
            color = "#6666aa") +
        xlab("AERONET AOD 470nm") +
        ylab("MAIAC AOD 470nm") +
        guides(color = "none") +
        facet_wrap(vars(comparison)) +
        theme_classic() +
        coord_equal(xlim = c(0, 1), ylim = c(0, 1), expand = F) +
        labs(caption = sprintf("Not shown: %s %s and %s %s",
           d[!in.region & comparison == "y.sat", .N],
           "points outside left panel",
           d[!in.region & comparison == "y.ground.pred", .N],
           "points outside right panel"))})()
```
